A Structural and Functional Bioinformatics Study of QTY-designed Retinylidene Proteins

### 2025-05-08 Paper/Source/manuscript.tex

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
	\caption{\textbf{The protein sequence alignments of 12 retinylidene proteins and their QTY analogs. } Blue: human opsins; purple: microbial opsins. The symbols $|$ and $*$ indicate that amino acids are identical and different respectively. Amino acids L, V, I and F in TM (transmembrane) alpha helices are replaced with Q, T, Y and Y respectively. The alpha helices (blue) are shown above the protein sequences. The characteristics of the proteins are shown above the sequences. 
    The alignments are: 
    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$, 
    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$, 
    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$, 
    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$, 
    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$. }
	\label{fig:sequences}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/superposition-human-pairwise.jpg}
	\caption{Superposition of AlphaFold3-predicted native human retinylidene proteins, their QTY analogs, and experimentally determined structures. 
    For \textbf{a)} to \textbf{i)}, green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure. The superpositions are 
    \textbf{a)} OPN1MW$^{\textrm{AF3}}$ \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW$^{\textrm{AF3}}$ \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW$^{\textrm{AF3}}$ \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2$^{\textrm{AF3}}$ \textit{vs} OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$, 
    \textbf{e)} OPN3$^{\textrm{AF3}}$ \textit{vs} OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4$^{\textrm{AF3}}$ \textit{vs} OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5$^{\textrm{AF3}}$ \textit{vs} OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR$^{\textrm{AF3}}$ \textit{vs} RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{QTY}}$, 
    \textbf{j)} BACR$^{\textrm{AF3}}$ \textit{vs} BACR$^{\textrm{QTY}}$, 
    \textbf{k)} BACH$^{\textrm{AF3}}$ \textit{vs} BACH$^{\textrm{QTY}}$, 
    \textbf{l)} ChR2$^{\textrm{AF3}}$ \textit{vs} ChR2$^{\textrm{QTY}}$. 
    For \textbf{j)} and \textbf{k)}, green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH. The superpositions are
    \textbf{j)} OPN1MW$^{\textrm{AF3}}$ \textit{vs} OPN1LW$^{\textrm{AF3}}$ \textit{vs} OPN1SW$^{\textrm{AF3}}$ \textit{vs} OPN2$^{\textrm{AF3}}$ \textit{vs} OPN3$^{\textrm{AF3}}$ \textit{vs} OPN4$^{\textrm{AF3}}$ \textit{vs} OPN5$^{\textrm{AF3}}$ \textit{vs} RGR$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{AF3}}$, 
    \textbf{k)} OPN1MW$^{\textrm{QTY}}$ \textit{vs} OPN1LW$^{\textrm{QTY}}$ \textit{vs} OPN1SW$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{QTY}}$ \textit{vs} OPN3$^{\textrm{QTY}}$ \textit{vs} OPN4$^{\textrm{QTY}}$ \textit{vs} OPN5$^{\textrm{QTY}}$ \textit{vs} RGR$^{\textrm{QTY}}$ \textit{vs} RRH$^{\textrm{QTY}}$. 
    }
	\label{fig:humansup}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/superposition-microbial.jpg}
	\caption{Superposition of microbial retinylidene proteins}
	\label{fig:microbialsup}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/hydrophobicity.jpg}
	\caption{Surface hydrophobicity}
	\label{fig:hydrophobicity}
\end{figure}

>>>>

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
        \vspace{-0.5cm}
	\caption{\textbf{The protein sequence alignments of 12 retinylidene proteins and their QTY analogs. } Blue: human opsins; purple: microbial opsins. The symbols $|$ and $*$ indicate that amino acids are identical and different respectively. Amino acids L, V, I and F in TM (transmembrane) alpha helices are replaced with Q, T, Y and Y respectively. The alpha helices (blue) are shown above the protein sequences. The characteristics of the proteins are shown above the sequences. 
    The alignments are: 
    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$, 
    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$, 
    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$, 
    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$, 
    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$. }
	\label{fig:sequences}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/superposition-human-pairwise.jpg}
	\caption{\textbf{Superposition of AlphaFold3-predicted native human retinylidene proteins, their QTY analogs, and experimentally determined structures. } For clarity, unstructured N- and C- terminal ends are deleted. 
    For \textbf{a)} to \textbf{i)}, green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure. The superpositions are 
    \textbf{a)} OPN1MW$^{\textrm{AF3}}$ \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW$^{\textrm{AF3}}$ \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW$^{\textrm{AF3}}$ \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2$^{\textrm{AF3}}$ \textit{vs} OPN2$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{EXP}}$, 
    \textbf{e)} OPN3$^{\textrm{AF3}}$ \textit{vs} OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4$^{\textrm{AF3}}$ \textit{vs} OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5$^{\textrm{AF3}}$ \textit{vs} OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR$^{\textrm{AF3}}$ \textit{vs} RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{QTY}}$. 
    For \textbf{j)} and \textbf{k)}, green: OPN1MW; red: OPN1LW; blue: OPN1SW; purple: OPN2; cyan: OPN3; gray: OPN4; olive: OPN5; orange: RGR; pink: RRH. The superpositions are
    \textbf{j)} OPN1MW$^{\textrm{AF3}}$ \textit{vs} OPN1LW$^{\textrm{AF3}}$ \textit{vs} OPN1SW$^{\textrm{AF3}}$ \textit{vs} OPN2$^{\textrm{AF3}}$ \textit{vs} OPN3$^{\textrm{AF3}}$ \textit{vs} OPN4$^{\textrm{AF3}}$ \textit{vs} OPN5$^{\textrm{AF3}}$ \textit{vs} RGR$^{\textrm{AF3}}$ \textit{vs} RRH$^{\textrm{AF3}}$, 
    \textbf{k)} OPN1MW$^{\textrm{QTY}}$ \textit{vs} OPN1LW$^{\textrm{QTY}}$ \textit{vs} OPN1SW$^{\textrm{QTY}}$ \textit{vs} OPN2$^{\textrm{QTY}}$ \textit{vs} OPN3$^{\textrm{QTY}}$ \textit{vs} OPN4$^{\textrm{QTY}}$ \textit{vs} OPN5$^{\textrm{QTY}}$ \textit{vs} RGR$^{\textrm{QTY}}$ \textit{vs} RRH$^{\textrm{QTY}}$. 
    }
	\label{fig:humansup}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/superposition-microbial.jpg}
	\caption{\textbf{Superposition of AlphaFold3-predicted native microbial retinylidene proteins, their QTY analogs, and experimentally determined structures. } For clarity, unstructured N- and C- terminal ends are deleted. 
    Green: AlphaFold3-predicted native structure; cyan: AlphaFold3-predicted QTY analog structure; magenta: experimentally determined structure. The superpositions are 
    \textbf{a)} BACR$^{\textrm{AF3}}$ \textit{vs} BACR$^{\textrm{QTY}}$ \textit{vs} BACR$^{\textrm{EXP}}$ monomer, 
    \textbf{b)} BACR$^{\textrm{AF3}}$ \textit{vs} BACR$^{\textrm{QTY}}$ \textit{vs} BACR$^{\textrm{EXP}}$ trimer, 
    \textbf{c)} BACH$^{\textrm{AF3}}$ \textit{vs} BACH$^{\textrm{QTY}}$ \textit{vs} BACH$^{\textrm{EXP}}$ monomer, 
    \textbf{d)} BACH$^{\textrm{AF3}}$ \textit{vs} BACH$^{\textrm{QTY}}$ \textit{vs} BACH$^{\textrm{EXP}}$ trimer, 
    \textbf{e)} ChR2$^{\textrm{AF3}}$ \textit{vs} ChR2$^{\textrm{QTY}}$ \textit{vs} ChR2$^{\textrm{EXP}}$ monomer, 
    \textbf{f)} ChR2$^{\textrm{AF3}}$ \textit{vs} ChR2$^{\textrm{QTY}}$ \textit{vs} ChR2$^{\textrm{EXP}}$ dimer. }
	\label{fig:microbialsup}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/hydrophobicity.jpg}
	\caption{\textbf{Hydrophobic surface of 12 retinylidene proteins and their water-soluble QTY analogs. } The native proteins have many hydrophobic (yellow) patches due to the presence of hydrophobic amino acids, including L, I, V, and F. After QTY substitution, hydrophilic Q, T, and Y have respectively replaced hydrophobic L, I/V, and F, and the hydrophobic patches in the surface of transmembrane helices have become more hydrophilic (cyan). For clarity, unstructured N- and C- terminal ends are deleted. 
    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$, 
    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$, 
    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$ monomer, 
    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$ monomer, 
    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$ monomer, 
    \textbf{m)} BACR \textit{vs} BACR$^{\textrm{QTY}}$ trimer, 
    \textbf{n)} BACH \textit{vs} BACH$^{\textrm{QTY}}$ trimer, 
    \textbf{o)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$ dimer. 
    }
	\label{fig:hydrophobicity}
\end{figure}
